### 2020-08-14 cases_and_policies/rmd/cf-pindex.Rmd

To compute the estimated and counterfactual paths we use the estimates
from column 2 of table \ref{tab:policy-cases}. We set initial $\Delta
\log \Delta C$ and $\log \Delta C$ to their values first observed in
the state we are simulating. We hold all other regressors at their
observed values. Error terms are drawn with replacement from the
residuals. We do this many times and report the average over draws of
the residuals. To calculate confidence intervals, we repeat the above
with coefficients drawn randomly from their asymptotic
distribution. The shaded region is a pointwise 90\% confidence
interval.

To be more precise, we can rewrite our regression model as:

$$
  Y_{it} = P_{it}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \epsilon_{it}
$$

where $Y_{it} = \log \Delta C_{it}$, $P_{it}$ are policies, and
$X_{it}$ are controls. Each counterfactual involves changing $P_{it}$
to some other value, $P_{it}^\ast$. We then generate counterfactual paths
for cases by in state $i$ conditional on
$Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast \}_{t=1}^T, \theta=(\alpha, \beta, \rho)$ by setting:

$$
  Y_{it}^{\ast,r} = {P_{it}^\ast}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \hat{\epsilon}_{it}^{\ast,r}
$$

where $\hat{\epsilon}_{it}^{\ast,r}$ are resampled with replacement
from $\{\hat{\epsilon}_{it}\}_{i=1,t=1}^{N,T}$. We do resample the
residuals $R$ times, repeating the above each time. We then compute

$$
\hat{E}[Y_{it}^\ast | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T, \theta] =
\frac{1}{R} \sum_{r=1}^R Y_{it}^{\ast,r}
$$

Finally, we repeatedly draw $\theta$ from its asymptotic distribution
and repeat all of the above to compute confidence intervals.

For case growth, the same procedure is used, but with $\Delta Y_{it} = \Delta \log \Delta C_{it}$ in place of $Y_{it}$. The top panel of the following figure shows

$$
E[\Delta Y_{it} | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}\}_{t=1}^T]
$$

and

$$
E[\Delta Y_{it}^\ast | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T]
$$

along with the observed $Y_{it}$, and the bottom panel shows the difference.

@@

To look at cases we instead compute,

$$
\hat{E}[\exp(Y_{it}^\ast) | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T, \theta] =
\frac{1}{R} \sum_{r=1}^R \exp(Y_{it}^{\ast,r})
$$

@@

### Holding Residuals fixed

In this subsection, instead of resampling residuals, we condition on them. That is we look at

$$
  Y_{it}^{\ast} = {P_{it}^\ast}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \hat{\epsilon}_{it}
$$

instead of

$$
  \frac{1}{R} \sum_{r=1}^R Y_{it}^{\ast,r}.
$$

```{r masks-resids-fixed}
simmodel1 <- function(st, samplecoefs=FALSE, nsim=1)
  simmodel(st, samplecoefs=samplecoefs, nsim=nsim,
           shockgen=NULL)
maskmodel1 <- function(st, samplecoefs=FALSE, nsim=1)
  maskmodel(st, samplecoefs=samplecoefs, nsim=nsim,
            shockgen=NULL)

rerunsim <- FALSE
if (!file.exists("cfmask1_idx.Rda") || rerunsim) {
  cfmasklist1 <- lapply(unique(df$state),
                        function(s) nopstatesim(s,simobs=simmodel1,simcf=maskmodel1, data=sdf, nresid=1))
  maskall1 <- rbindlist(lapply(cfmasklist1, getmeans))
  save(cfmasklist1, maskall1, file="cfmask1_idx.Rda")
}
load("cfmask1_idx.Rda")
cfmask1 <- do.call(rbind, lapply(cfmasklist1, function(x) x$edf))

for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfmask1, yvar="deaths", data=df)
  print(f$figp +  ggtitle(sprintf("Effect of mandating masks on April 1st in %s",st)))

}

figs1 <- nationalplots(maskall1, cfmask1, "mandating masks on April 1st\n")

for (f in figs1) print(f)
```

@@

```{r home, cache=FALSE}
cf <- df
cf[,"pindex"] <- 0
cf <- subset(cf, cf$date>=datelims[1]) #+L)
noshelter <- createforwardsim(m, cf)

if (!file.exists("cfindex_idx.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfindex_idx.Rda")
}
load("cfindex_idx.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

```{r, cache=TRUE}
cfshelter <- merge(cfshelter, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfshelter, data=df)
  print(f$figp +  ggtitle(sprintf("Effect of no shutdown policies in %s",st)))

@@

figs <- nationalplots(shelterall, cfshelter, "no shutdown policies")

@@

```{r home-deaths, cache=FALSE}
cf <- df
cf[,"pindex"] <- 0
cf <- subset(cf, cf$date>=datelims[1]) #+L)
noshelter <- createforwardsim(m, cf, dvar="dlogdd", var="logdd")

if (!file.exists("cfindex_deaths_idx.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfindex_deaths_idx.Rda")
}
load("cfindex_deaths_idx.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

```{r, cache=TRUE}
cfshelter <- merge(cfshelter, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfshelter, data=df, yvar="deaths")
  print(f$figp +  ggtitle(sprintf("Effect of no shutdown policies in %s",st)))

@@

figs <- nationalplots(shelterall, cfshelter, "no shutdown policies", yvar="deaths")

>>>>

@@

@@

@@

```{r home, cache=FALSE}
cf <- df
cf[,"pindex"] <- 0
cf <- subset(cf, cf$date>=datelims[1]) #+L)
noindex <- createforwardsim(m, cf)

if (!file.exists("cfindex_idx.Rda") || rerunsim) {
  cfindexlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noindex, data=sdf))
  indexall <- rbindlist(lapply(cfindexlist, getmeans))
  save(cfindexlist, indexall, file="cfindex_idx.Rda")
}
load("cfindex_idx.Rda")
cfindex <- do.call(rbind, lapply(cfindexlist, function(x) x$edf))
```

```{r, cache=TRUE}
cfindex <- merge(cfindex, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfindex, data=df)
  print(f$figp +  ggtitle(sprintf("Effect of no shutdown policies in %s",st)))

@@

figs <- nationalplots(indexall, cfindex, "no shutdown policies")

@@

```{r home-deaths, cache=FALSE}
cf <- df
cf[,"pindex"] <- 0
cf <- subset(cf, cf$date>=datelims[1]) #+L)
noindex <- createforwardsim(m, cf, dvar="dlogdd", var="logdd")

if (!file.exists("cfindex_deaths_idx.Rda") || rerunsim) {
  cfindexlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noindex, data=sdf))
  indexall <- rbindlist(lapply(cfindexlist, getmeans))
  save(cfindexlist, indexall, file="cfindex_deaths_idx.Rda")
}
load("cfindex_deaths_idx.Rda")
cfindex <- do.call(rbind, lapply(cfindexlist, function(x) x$edf))
```

```{r, cache=TRUE}
cfindex <- merge(cfindex, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfindex, data=df, yvar="deaths")
  print(f$figp +  ggtitle(sprintf("Effect of no shutdown policies in %s",st)))

@@

figs <- nationalplots(indexall, cfindex, "no shutdown policies", yvar="deaths")

### 2020-08-14 cases_and_policies/rmd/counterfactuals.Rmd

rerunsim=FALSE
if (!file.exists("cfnop.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(sdf$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel,data=sdf))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop.Rda")
}
load("cfnop.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

@@

To compute the estimated and counterfactual paths we use the estimates
from column 2 of table \ref{tab:policy-cases}. We set initial $\Delta
\log \Delta C$ and $\log \Delta C$ to their values first observed in
the state we are simulating. We hold all other regressors at their
observed values. Error terms are drawn with replacement from the
residuals. We do this many times and report the average over draws of
the residuals. To calculate confidence intervals, we repeat the above
with coefficients drawn randomly from their asymptotic
distribution. The shaded region is a pointwise 90\% confidence
interval.

To be more precise, we can rewrite our regression model as:

$$
  Y_{it} = P_{it}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \epsilon_{it}
$$

where $Y_{it} = \log \Delta C_{it}$, $P_{it}$ are policies, and
$X_{it}$ are controls. Each counterfactual involves changing $P_{it}$
to some other value, $P_{it}^\ast$. We then generate counterfactual paths
for cases by in state $i$ conditional on
$Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast \}_{t=1}^T, \theta=(\alpha, \beta, \rho)$ by setting:

$$
  Y_{it}^{\ast,r} = {P_{it}^\ast}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \hat{\epsilon}_{it}^{\ast,r}
$$

where $\hat{\epsilon}_{it}^{\ast,r}$ are resampled with replacement
from $\{\hat{\epsilon}_{it}\}_{i=1,t=1}^{N,T}$. We do resample the
residuals $R$ times, repeating the above each time. We then compute

$$
\hat{E}[Y_{it}^\ast | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T, \theta] =
\frac{1}{R} \sum_{r=1}^R Y_{it}^{\ast,r}
$$

Finally, we repeatedly draw $\theta$ from its asymptotic distribution
and repeat all of the above to compute confidence intervals.

For case growth, the same procedure is used, but with $\Delta Y_{it} = \Delta \log \Delta C_{it}$ in place of $Y_{it}$. The top panel of the following figure shows

$$
E[\Delta Y_{it} | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}\}_{t=1}^T]
$$

and

$$
E[\Delta Y_{it}^\ast | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T]
$$

along with the observed $Y_{it}$, and the bottom panel shows the difference.

@@

if (!file.exists("cfnb.Rda") || rerunsim) {
  cfnblist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=nobmodel, data=sdf))
  nball <- rbindlist(lapply(cfnblist, getmeans))
  save(cfnblist,nball, file="cfnb.Rda")
}
load("cfnb.Rda")
cfnb <- do.call(rbind, lapply(cfnblist, function(x) x$edf))
```

@@

if (!file.exists("cfmask.Rda") || rerunsim) {
  cfmasklist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=maskmodel, data=sdf))
  maskall <- rbindlist(lapply(cfmasklist, getmeans))
  save(cfmasklist, maskall, file="cfmask.Rda")
}
load("cfmask.Rda")
cfmask <- do.call(rbind, lapply(cfmasklist, function(x) x$edf))
```

@@

### Holding Residuals fixed

In this subsection, instead of resampling residuals, we condition on them. That is we look at

$$
  Y_{it}^{\ast} = {P_{it}^\ast}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \hat{\epsilon}_{it}
$$

instead of

$$
  \frac{1}{R} \sum_{r=1}^R Y_{it}^{\ast,r}.
$$

```{r masks-resids-fixed}
simmodel1 <- function(st, samplecoefs=FALSE, nsim=1)
  simmodel(st, samplecoefs=samplecoefs, nsim=nsim,
           shockgen=NULL)
maskmodel1 <- function(st, samplecoefs=FALSE, nsim=1)
  maskmodel(st, samplecoefs=samplecoefs, nsim=nsim,
            shockgen=NULL)

rerunsim <- FALSE
if (!file.exists("cfmask1.Rda") || rerunsim) {
  cfmasklist1 <- lapply(unique(df$state),
                        function(s) nopstatesim(s,simobs=simmodel1,simcf=maskmodel1, data=sdf, nresid=1))
  maskall1 <- rbindlist(lapply(cfmasklist1, getmeans))
  save(cfmasklist1, maskall1, file="cfmask1.Rda")
}
load("cfmask1.Rda")
cfmask1 <- do.call(rbind, lapply(cfmasklist1, function(x) x$edf))

for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfmask1, yvar="deaths", data=df)
  print(f$figp +  ggtitle(sprintf("Effect of mandating masks on April 1st in %s",st)))

}

figs1 <- nationalplots(maskall1, cfmask1, "mandating masks on April 1st\n")

for (f in figs1) print(f)
```

@@

if (!file.exists("cfshelter.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfshelter.Rda")
}
load("cfshelter.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

@@

@@

@@

@@

## Non Essential Business Closures

@@

>>>>

rerunsim=FALSE
if (!file.exists("cfnop.Rda") || rerunsim) {
  cfnoplist <- lapply(unique(sdf$state), function(s)
    nopstatesim(s,simobs=simmodel,simcf=nopmodel,data=sdf, nresid=1))
  allmeans <- rbindlist(lapply(cfnoplist, getmeans))
  save(cfnoplist,allmeans, file="cfnop.Rda")
}
load("cfnop.Rda")
cfnop <- do.call(rbind, lapply(cfnoplist, function(x) x$edf))
```

@@

We hold residuals fixed throughout.
<!-- To compute the estimated and counterfactual paths we use the estimates -->
<!-- from column 2 of table \ref{tab:policy-cases}. We set initial $\Delta -->
<!-- \log \Delta C$ and $\log \Delta C$ to their values first observed in -->
<!-- the state we are simulating. We hold all other regressors at their -->
<!-- observed values. Error terms are drawn with replacement from the -->
<!-- residuals. We do this many times and report the average over draws of -->
<!-- the residuals. To calculate confidence intervals, we repeat the above -->
<!-- with coefficients drawn randomly from their asymptotic -->
<!-- distribution. The shaded region is a pointwise 90\% confidence -->
<!-- interval. -->

<!-- To be more precise, we can rewrite our regression model as: -->

<!-- $$ -->
<!--   Y_{it} = P_{it}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \epsilon_{it} -->
<!-- $$ -->

<!-- where $Y_{it} = \log \Delta C_{it}$, $P_{it}$ are policies, and -->
<!-- $X_{it}$ are controls. Each counterfactual involves changing $P_{it}$ -->
<!-- to some other value, $P_{it}^\ast$. We then generate counterfactual paths -->
<!-- for cases by in state $i$ conditional on -->
<!-- $Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast \}_{t=1}^T, \theta=(\alpha, \beta, \rho)$ by setting: -->

<!-- $$ -->
<!--   Y_{it}^{\ast,r} = {P_{it}^\ast}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \hat{\epsilon}_{it}^{\ast,r} -->
<!-- $$ -->

<!-- where $\hat{\epsilon}_{it}^{\ast,r}$ are resampled with replacement -->
<!-- from $\{\hat{\epsilon}_{it}\}_{i=1,t=1}^{N,T}$. We do resample the -->
<!-- residuals $R$ times, repeating the above each time. We then compute -->

<!-- $$ -->
<!-- \hat{E}[Y_{it}^\ast | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T, \theta] = -->
<!-- \frac{1}{R} \sum_{r=1}^R Y_{it}^{\ast,r} -->
<!-- $$ -->

<!-- Finally, we repeatedly draw $\theta$ from its asymptotic distribution -->
<!-- and repeat all of the above to compute confidence intervals. -->

<!-- For case growth, the same procedure is used, but with $\Delta Y_{it} = \Delta \log \Delta C_{it}$ in place of $Y_{it}$. The top panel of the following figure shows -->

<!-- $$ -->
<!-- E[\Delta Y_{it} | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}\}_{t=1}^T] -->
<!-- $$ -->

<!-- and -->

<!-- $$ -->
<!-- E[\Delta Y_{it}^\ast | Y_{i1}, ..., Y_{iL}, \{X_{it}, P_{it}^\ast\}_{t=1}^T] -->
<!-- $$ -->

<!-- along with the observed $Y_{it}$, and the bottom panel shows the difference. -->

<!-- In this subsection, instead of resampling residuals, we condition on them. That is we look at -->

<!-- $$ -->
<!--   Y_{it}^{\ast} = {P_{it}^\ast}'\alpha + \sum_{\ell=1}^L \rho_\ell Y_{it-\ell} + X_{it}'\beta + \hat{\epsilon}_{it} -->
<!-- $$ -->

<!-- instead of -->

<!-- $$ -->
<!--   \frac{1}{R} \sum_{r=1}^R Y_{it}^{\ast,r}. -->
<!-- $$ -->

@@

if (!file.exists("cfnb.Rda") || rerunsim) {
  cfnblist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=nobmodel, data=sdf, nresid=1))
  nball <- rbindlist(lapply(cfnblist, getmeans))
  save(cfnblist,nball, file="cfnb.Rda")
}
load("cfnb.Rda")
cfnb <- do.call(rbind, lapply(cfnblist, function(x) x$edf))
```

@@

if (!file.exists("cfmask.Rda") || rerunsim) {
  cfmasklist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=maskmodel, data=sdf, nresid=1))
  maskall <- rbindlist(lapply(cfmasklist, getmeans))
  save(cfmasklist, maskall, file="cfmask.Rda")
}
load("cfmask.Rda")
cfmask <- do.call(rbind, lapply(cfmasklist, function(x) x$edf))
```

@@

@@

if (!file.exists("cfshelter.Rda") || rerunsim) {
  cfshelterlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noshelter, data=sdf, nresid=1))
  shelterall <- rbindlist(lapply(cfshelterlist, getmeans))
  save(cfshelterlist, shelterall, file="cfshelter.Rda")
}
load("cfshelter.Rda")
cfshelter <- do.call(rbind, lapply(cfshelterlist, function(x) x$edf))
```

@@

## Shutdown policies

We now look at what happens if the four shutdown policies in pindex were never implemented.

```{r shutdown, cache=FALSE}
cf <- df
cf[,"pshelter"] <- 0
cf[,"pmovie"] <- 0
cf[,"prestaurant"] <- 0
cf[,"pnonessential"] <- 0
cf <- subset(cf, cf$date>=datelims[1]) #+L)
noindex <- createforwardsim(m, cf)

if (!file.exists("cfindex.Rda") || rerunsim) {
  cfindexlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noindex, data=sdf, nresid=1))
  indexall <- rbindlist(lapply(cfindexlist, getmeans))
  save(cfindexlist, indexall, file="cfindex.Rda")
}
load("cfindex.Rda")
cfindex <- do.call(rbind, lapply(cfindexlist, function(x) x$edf))
```

```{r, cache=TRUE}
cfindex <- merge(cfindex, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfindex, data=df, yvar="deaths")
  print(f$figp +  ggtitle(sprintf("Effect of no shutdown policies in %s",st)))

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dgrowth.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcases.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

figs <- nationalplots(indexall, cfindex, "no shutdown policies", yvar="deaths")

figdev(paste(rootdir,"tex/tables_and_figures/us-index-dgrowth.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-index-dcases.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-index-rel.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()

@@

## Removing Policies

@@

### National

@@

## Non-essential Business Closures

@@

## Shutdown policies

We now look at what happens if the four shutdown policies in pindex were never implemented.

```{r shutdown-deaths, cache=FALSE}
cf <- df
cf[,"pshelter"] <- 0
cf[,"pmovie"] <- 0
cf[,"prestaurant"] <- 0
cf[,"pnonessential"] <- 0
cf <- subset(cf, cf$date>=datelims[1]) #+L)
noindex <- createforwardsim(m, cf, dvar="dlogdd", var="logdd")

if (!file.exists("cfindex_deaths.Rda") || rerunsim) {
  cfindexlist <- lapply(unique(df$state), function(s) nopstatesim(s,simobs=simmodel,simcf=noindex, data=sdf))
  indexall <- rbindlist(lapply(cfindexlist, getmeans))
  save(cfindexlist, indexall, file="cfindex_deaths.Rda")
}
load("cfindex_deaths.Rda")
cfindex <- do.call(rbind, lapply(cfindexlist, function(x) x$edf))
```

```{r, cache=TRUE}
cfindex <- merge(cfindex, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfindex, data=df, yvar="deaths")
  print(f$figp +  ggtitle(sprintf("Effect of no shutdown policies in %s",st)))

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dgrowth_deaths.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-index-dcases_deaths.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}

figs <- nationalplots(indexall, cfindex, "no shutdown policies", yvar="deaths")

figdev(paste(rootdir,"tex/tables_and_figures/us-index-dgrowth_deaths.pdf",sep="/"), width=5,height=3.75)
figs$g
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-index-dcases_deaths.pdf",sep="/"), width=5,height=3.75)
figs$c
dev.off()

figdev(paste(rootdir,"tex/tables_and_figures/us-index-rel_deaths.pdf",sep="/"), width=5,height=3.75)
figs$r
dev.off()
